```{r}
rm(list=ls())
set.seed(133)
```

```{r setup-packages}
LIST_packages<-c("extRemes","distillery","Lmoments","ggplot2","reshape2"         ,"mev","POT"  ,"roxygen2")
for (pkg in LIST_packages) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg)  # Install if not already installed
    library(pkg, character.only = TRUE)  # Load the package
  }
}
```


```{r}
### Import functions
source("fonctions/fonctions.R")
```

## Simulation step
To illustrate the effect of asymptotic dependence (AD) and asymptotic independence (AI), we will simulate realizations of the logistic model of parameter $\alpha$. 
This model will generate regularly varying vectors, which means that we can apply a polar decomposition on the law of extreme events. 
In this context, we can choose the case studied thanks to the value of $\alpha$. If $\alpha=1$, we get AI. Otherwise, we get AD. 
```{r}
d<-2
### alpha_dep=1 <=> Asymp indep
### alpha_dep>0
alpha_dep<-0.5
if(alpha_dep==1){
  print("Independence in mev laws= > Asymp Independence (AI)")
}else{
  print("Dependence in mev laws = > Asymp Dependence (AD)")
}
```

```{r}
Vect_U_V<-mev::rmev(n = 10000,d = d,param = alpha_dep^(-1)
          ,model = "log")
plot(Vect_U_V,log="xy",
     xlab="First coordinate",
     ylab="Second coordinate",
     main="Simulations from the mev law")
```
## Choice of the risk function
Define what is an extreme event thanks to a homogeneous function. 
```{r}
## Choose a homogeneous function.
name_function<-"max"
if(name_function=="min"){
  Rfun<-function(x){return(min(x))}
}
if(name_function=="max"){
  Rfun<-function(x){return(max(x))}
}
## Build your own homogeneous function.
#Rfun<-function(x){return(...(x))}

```
## Observe the effect of the AD/AI on extremes

```{r}
Var<-apply(X = Vect_U_V,MARGIN = 1,FUN = Rfun)
Min_<-apply(X = Vect_U_V,MARGIN = 1,FUN = min)
Max_<-apply(X = Vect_U_V,MARGIN = 1,FUN = max)

Graphics_estimators_gamma(series = Var,
                          vect_k = c(10:400),
                          Title_graphic = "Shape param of R_f",
                          y_lims = c(0,2))

```
```{r}
GG1<-Graphics_estimators_gamma(series = Min_,
                          vect_k = c(10:400),
                          Title_graphic = "Shape param of minimum",
                          y_lims = c(0,2))
```

```{r}
GG2<-Graphics_estimators_gamma(series = Max_,
                          vect_k = c(10:400),
                          Title_graphic = "Shape param of maximum",
                          y_lims = c(0,2))
```

We find $\gamma_{\max}=\gamma_{\min}=1$ if AD 
, $\gamma_{\max}=1$ and $\gamma_{\min}<1$ if AI. 
Thus, the choice of AD/AI does has an effect on $\gamma_{\min}$ but does not have an effect on $\gamma_{\max}$. 

## Extreme events
```{r}

kopt<-150
u_th<-quantile(Var,1-(kopt/nrow(Vect_U_V)))
Inds_extremes<-which(Var>u_th)
Obs_exts<-Vect_U_V[Inds_extremes,]
plot(Obs_exts,log="xy")
Var_exts<-Var[Inds_extremes]
```
## Compute angular components. 
The choice of AI/AD does have an impact on the shape parameter but it also has an impact on the marginals of the angular law. 
```{r}
ANG_comp<-t(t(Obs_exts)%*%diag(Var_exts^(-1)))
TITLE_descrip<-ifelse(alpha_dep==1,yes = "Degenerate laws if maximum used",no ="Non degenerate laws")
plot(ANG_comp,xlab="w_1",ylab="w_2",
     main=TITLE_descrip)

```

```{r}
summary(ANG_comp)
```

We see that we directly get degenerate marginals if we combine maximum and asymptotic independence $(0,1)$ and $(1,0)$.
If we use the minimum, we will always have non degenerate marginals $(x,1)$ and $(1,y)$.
```{r}
if(name_function!="min"){
  plot(density(acos(ANG_comp[,1])),main="Angular density of U vs V (Theta of the polar decomp)")
}

```

```{r}
if(name_function!="min"){
  plot(density(asin(ANG_comp[,2])),main="Angular density of U vs V (Theta of the polar decomp, with second coord)")
}
```


```{r}
if(alpha_dep==1){
  print("peaks at x=0 and x=pi/2, we are on the axes if we use the maximum !")
}else{
  print("no specific peaks")
}
```

